Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
s/n always math mode

This idea, dubbed ``chemical tagging'', was proposed long ago
\citep{freeman} and is one of the principal motivations for a number
of surveys, most notably \apogee\ \citep{apogee},
\gaiaeso\ \citep{gaiaeso} and \galah\ \citep{galah}.
In order to determine the precise abundance labels for chemical
tagging, these surveys are each measuring high-resolution, high
signal-to-noise (S/N) spectra for hundreds of thousands of stars across the
Galaxy's disk, bulge and halo.

>>>>

This idea, dubbed ``chemical tagging'', was proposed long ago
\citep{freeman} and is one of the principal motivations for a number
of surveys, most notably \apogee\ \citep{apogee},
\gaiaeso\ \citep{gaiaeso} and \galah\ \citep{galah}.
In order to determine the precise abundance labels for chemical
tagging, these surveys are each measuring high-resolution, high
signal-to-noise ($S/N$) spectra for hundreds of thousands of stars across the
Galaxy's disk, bulge and halo.
